---
title: "Lab_7"
author: "Renee LaManna"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore penguins

Use `GGally:ggpairs()` to create pairs plot. 

```{r}
ggpairs(penguins)
```

This graph is kind of overkill. Lets simplify variables we include in our ggpairs plot:

-species
-bill_length_mm through body_mass_g
-keeping species AND bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```
Scatter plot: intersection of 2 species explains relationship?
Quick way to look at multi variable comparisons and add some groupings


## Multiple linear regression 

We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome variable which is penguin body mass

The different predictor variable we are going to try are:

- species
- flipper length
- sex
- bill length

### Model 1

Model body mass based on only flipper length and bill depth (bad idea, need to look at other important variables that are currently missing, such as sex)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients:
model_1

summary(model_1)
```

If everything else is held constant, for every 1 mm increase flipper length, we expect on average penguins body mass to increase by 51.54 grams if everything else is held constant `r model_1$flipper_length_mm`

76% of variance in penguin body mass (dependent variable) is explained by this model which contains these 2 variable (can also write out these variables.

There is still 24% that is not explained, might be missing some important variables (such as species or sex) that explain remaining of variance


Actually -- we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

# Let's call coefficients 
model_2

```
Can only inteprete coeffficents with respect to reference levels? 
What is the reference level?
Female = 0
Adeline = 0

# Try intepretate coeffiecients for 

On average, we expect a gentoo penguin to be 836 grams larger than an adeline if everything else is the same
On average, we expect a male penguin to be 530 grams larger than a female penguin if everything else is the same


## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)
```
Males seem to have a higher body mass on average. Shift will be around 530.38 grams in increase
We expect on average Gentoo to be 836 grams greater than adeline 
Chinstrap have 87.62 lower body mass than adeline (not a very big difference, so difficult to see)

## A couple ways to get and report MLR model outcomes

Use broom::tidy() to get model coefficient info in a tidy data frame

```{r}
penguin_model2_coef <- tidy(model_2)

penguin_model2_coef
```

Try to write inline code that spits out coefficient for gentoo

`r penguin_model2_coef$estimate` call entire estimate coloumn
`r penguin_model2_coef$estimate[4]` call 4th element, estimate associated with speciesGentoo

## Look at model diagnostics

Use the plot() function

```{r}
plot(model_2)

summary(model_2)

```
- R2 value is much greater after adding sex and species


## Report the model outputs in a summary table

Use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer - lets it know it will already produce an html output

```{r, results = "asis"}
stargazer(model_2, model_1, type = "html")
```

